\documentclass[11pt,a4paper]{article}

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{enumerate}
\usepackage[margin=1in]{geometry}
\setlength\parindent{0pt}
\usepackage{multicol}


\title{%
    \textbf{Advanced Topics in Control 2020: \\ Large-Scale Convex Optimization} \\[.5em]
    Solution to Exercise 10
}
\author{Goran Banjac, Mathias Hudoba de Badyn, Andrea Iannelli, \\ Angeliki Kamoutsi, Ilnura Usmanova}
\date{\today}

\begin{document}
\maketitle
\hrule
\vspace{0.3cm}




\section{Problem 1}

\begin{enumerate}
  \item User 25 would very much like \textit{Pokemon Advanced Generation: Rekkuu no Houmonsha Deoxys}, as the predicted rating is 7.467.
  \item The top 10 animes Mathias should watch have IDs            2,
         137,
           8,
           9,
        2154,
          32,
          12,
          91,
          20, and
         122.
         The top 5 that aren't already rated by Mathias are:
    \begin{enumerate}
      \item 8: \emph{Code Geass: Hangyaku no Lelouch R2}
      \item 9: \emph{Code Geass: Hangyaku no Lelouch}
      \item 32: \emph{Psycho-Pass}
      \item 12: \emph{Suzumiya Haruhi no Shoushitsu}
      \item 91: \emph{Zetsuen no Tempest}.
    \end{enumerate}
  \item After rating \emph{Mahou Shoujo Madoka$\star$Magica} a 9/10, the top 10 animes that Mathias should watch have IDs            2,
         137,
          31,
         350,
          71,
           8,
          40,
        2154,
         237, and
          62.
          The top 5 that aren't already rated by Mathias are now:
\begin{enumerate}
  \item 350: \emph{Bobobo-bo Bo-bobo}
  \item 71: \emph{Darker than Black: Kuro no Keiyakusha}
  \item 8: \emph{Code Geass: Hangyaku no Lelouch R2}
  \item 40: \emph{Higurashi no Naku Koro ni Kai}
  \item 237: \emph{Mobile Police Patlabor: On Television}
\end{enumerate}
Almost all of the recommendations changed.
This is absolutely a great feature: as my preferences become more clear and I watch more animes and rate them, the algorithm will update the recommendations with new animes that I haven't seen. 
This will make me more addicted to anime, thus leading to me giving more money to the streaming website.

\item The top 10 Sci-Fi animes that Mathias should watch have IDs (in the Sci-Fi-only dataset) 
          99,
           2,
           8,
          51,
        2006,
           9,
         311,
          25,
          69, and
          12.
The top 5 that Mathias hasn't already rated are:
\begin{enumerate}
  \item 8: \emph{Code Geass: Hangyaku no Lelouch R2}
  \item 51: \emph{Darker than Black: Kuro no Keiyakusha}
  \item 9: \emph{Code Geass: Hangyaku no Lelouch}
  \item 311: \emph{Neon Genesis Evangelion: Death \& Rebirth}
  \item 25:  \emph{Psycho-Pass}
\end{enumerate}
Some of these are recommended from the other dataset, suggesting that Mathias' recommendations are highly correlated to the Sci-Fi genre.
The animes which are expected for Mathias to rate higher than a 6 are:
\begin{itemize}
\item  \emph{    Steins;Gate   }                                      
\item  \emph{       Gintama Movie: Kanketsu-hen - Yorozuya yo Eien Nare }
\item  \emph{       Code Geass: Hangyaku no Lelouch R2        }          
\item  \emph{       Code Geass: Hangyaku no Lelouch            }         
\item  \emph{       Cowboy Bebop                               }         
\item  \emph{       One Punch Man                               }        
\item  \emph{       Suzumiya Haruhi no Shoushitsu                }       
\item  \emph{       Tengen Toppa Gurren Lagann                    }      
\item  \emph{       Steins;Gate Movie: Fuka Ryouiki no Déjà vu     }     
\item  \emph{       Kiseijuu: Sei no Kakuritsu                      }    
\item  \emph{       Evangelion: 2.0 You Can (Not) Advance            }   
\item  \emph{       Psycho-Pass                                       }  
\item  \emph{       Steins;Gate: Oukoubakko no Poriomania              } 
\item  \emph{       Neon Genesis Evangelion: The End of Evangelion }     
\item  \emph{       Toki wo Kakeru Shoujo                           }    
\item  \emph{       Tenkuu no Shiro Laputa                           }   
\item  \emph{       Ghost in the Shell                                }  
\item  \emph{       Neon Genesis Evangelion                          }   
\item  \emph{       Trigun                                            }  
\item  \emph{       Summer Wars                                       }  
\item  \emph{       Darker than Black: Kuro no Keiyakusha              } 
\item  \emph{       Sakasama no Patema                                  }
\item  \emph{       Interstella5555: The 5tory of The 5ecret 5tar 5ystem}
\item  \emph{       Akira                                               }
\item  \emph{       Paprika                                             }
\item  \emph{       Wolfs Rain OVA                               } 
\item  \emph{       Darker than Black: Kuro no Keiyakusha Gaiden   }     
\item  \emph{       Ergo Proxy                                      }    
\item  \emph{       Serial Experiments Lain                          }   
\item  \emph{       Gundam Build Fighters                             }  
\item  \emph{       Mobile Suit Gundam Seed                            } 
\item  \emph{       Wolfs Rain                                    }
\item  \emph{       Kumo no Mukou, Yakusoku no Basho                }    
\item  \emph{       Toaru Majutsu no Index II                        }   
\item  \emph{       Tsuritama                                         }  
\item  \emph{       No.6                                               } 
\item  \emph{       Toaru Majutsu no Index: Endymion no Kiseki          }
\item  \emph{       Toaru Majutsu no Index                              }
\item  \emph{       Aldnoah.Zero                               }         
\item  \emph{       Bobobo-bo Bo-bobo                           }        
\item  \emph{       Neon Genesis Evangelion: Death \& Rebirth    }    
\item  \emph{       Deadman Wonderland                            }      
\item  \emph{       Final Fantasy VII: Last Order                  }     
\item  \emph{       Saishuu Heiki Kanojo                            }    
\item  \emph{       Dragon Ball GT                                   }   
\item  \emph{       Steins;Gate 0   }
\end{itemize}

\item This is not a good idea. You are losing a lot of information by switching to a binary recommender, and the solution is also poorly scaled and it takes longer to solve.
One pro is that the actual data can be saved as a boolean rather than an integer, and so one can store orders of magnitude more data this way.
It is also no longer possible to rank animes, since they are labeled ``recommend'' or ``do not recommend''.

Most of the animes that were recommended in the top 5 are also recommended now, but the solution spits out far to many animes to include in this PDF.

\end{enumerate}


\end{document}
